\documentclass{homework}
\course{Math 5522H}
\author{Jim Fowler}
\input{preamble}

\begin{document}
\maketitle

\begin{inspiration}
Nature laughs at the difficulties of integration.
\byline{Pierre-Simon Laplace} % what's the original source for this quotation?
\end{inspiration}

\section{Terminology}

\begin{problem}
  What does it mean to say that $\Omega \subset \C$ is connected?  Is path-connected?  
\end{problem}

\begin{problem}
  What is a piecewise-smooth \textbf{curve}?  When are two curves ``the same''?  
\end{problem}

\begin{problem}
    Define $\int_\gamma f(z) \, dz$ and define $\int_\gamma f(z) \, dx$ and define $\int_\gamma f(z) \, dy$.
\end{problem}

\begin{problem}
  Define $\int_\gamma f(z) \, d\conj{z}$.
\end{problem}

\begin{problem}
  Define $\int_\gamma f(z) \, \abs{dz}$.
\end{problem}

\begin{problem}
  What does it mean to say that a $1$-form is \textbf{exact}?
\end{problem}

\begin{problem}
  What are the \textbf{poles} and \textbf{zeros} of a rational
  function $p(z)/q(z)$?
\end{problem}

\section{Numericals}

\begin{problem}Consider a piecewise smooth curve $\gamma$ tracing the boundary of the square
  $$S = \{ z = x+iy\in \C : \abs{x} \mbox{ and } \abs{y} \leq 1 \}.$$
  Compute $\displaystyle\int_\gamma \frac{1}{z} \, dz$ by hand.
\end{problem}

\begin{problem}\label{integral-powers-of-z}Consider the curve $\gamma : [0,2\pi] \to \C$ given by $\gamma(\theta) = e^{i\theta}$.  For an integer $n \in \Z$, compute $\displaystyle\int_\gamma z^n \, dz$ and $\displaystyle\int_\gamma \conj{z}^n \, dz$.
\end{problem}

\begin{problem}\label{one-over-z-around-circle}Let $\gamma$ be a (positively oriented) parametrization of a circle
  in the plane, and suppose the image of $\gamma$ does not include the
  origin.  Compute $\displaystyle\int_\gamma \frac{1}{z} \, dz$.
\end{problem}

\begin{problem}\label{lacunary-series}What is radius $R$ of convergence of
  $\displaystyle\sum_{n=1} x^{(n!)}$?  (This is a \textbf{lacunary
    series} with large gaps between nonzero terms.)
\end{problem}

% primitives

\section{Exploration}

\begin{problem}For the series in \ref{lacunary-series}, find a dense
  subset of the circle $\{ z \in \C : \abs{z} = R \}$ where the series
  diverges.
\end{problem}
  
\begin{problem}
  For which $z \in \C$ with $|z|=1$ does the series
  $\displaystyle\sum_{n=0}^{\infty} \frac{z^n}{n}$ converge?  Diverge?
\end{problem}

\begin{problem}Suppose $f : \C \to \C$ is a rational function which
  sends the unit circle to the real line, i.e., for $z \in \C$ with
  $|z| = 1$ we have $f(z) \in \R$.  Inspired
  by \ref{schwarz-reflection-principle}, compute
  $\overline{f(1/\conj{z})}$ and then discuss the relationship between
  the poles and zeros of $f$.
\end{problem}

\begin{problem}In lecture, we briefly saw an example (the
  \textbf{topologist's sine curve}) of a subset of $\mathbb{C}$ which
  is connected but not path-connected.  For open subsets of
  $\mathbb{C}$, what is the relationship between connectedness and
  path-connectedness?
\end{problem}

\begin{problem}\label{argument-principle-numerical}Consider $\gamma : [0,2\pi] \to \C$ given by $\gamma(\theta) = e^{i\theta}$.  For an integer $n \in \Z$ and $f(z) = z^n$, compute
  \[
    \frac{1}{2\pi i} \displaystyle\int_\gamma \frac{f'(z)}{f(z)} \, dz
  \]
  in two different ways.  First, evaluate $f'(z)/f(z)$ and invoke
  \ref{integral-powers-of-z}.  Second, describe a curve $\gamma_n$ and
  interpret $\int_\gamma \frac{f'(z)}{f(z)} \, dz$ as
  $\int_{\gamma_n} dz/z$ for that different curve $\gamma_n$.  (This
  is our first glimpse of the \textbf{argument principle}.)
\end{problem}

\begin{problem}
  Consider the curve $\gamma : [0,2\pi] \to \C$ given by $\gamma(\theta) = e^{i\theta}$.  For $w \in \C$ with $|w| \neq 1$, compute
  \[
    \frac{1}{2\pi i} \displaystyle\int_\gamma \frac{1}{z-w} \, dz
  \]
  perhaps by invoking \ref{one-over-z-around-circle}.
\end{problem}

\begin{problem}
  Yet again consider the curve $\gamma : [0,2\pi] \to \C$ given by $\gamma(\theta) = e^{i\theta}$.  For distinct $w_1, w_2 \in \C$ with $\abs{w_1} \neq 1$ and $\abs{w_2} \neq 1$, let $f(z) = (z - w_1) (z - w_2)$ and compute
  \[
    \frac{1}{2\pi i} \displaystyle\int_\gamma \frac{f'(z)}{f(z)} \, dz.
  \]
\end{problem}

\section{Prove or Disprove and Salvage if Possible}

\begin{problem}
  If $e^z = e^w$, then $z = w$.
\end{problem}

\begin{problem}
  If $f \, dz$ is exact, then $\displaystyle\int_\gamma f \, dz = 0$.
\end{problem}

\begin{problem}% orientation issues
  Suppose $\gamma : [0,1] \to \C$ is a smooth curve, and $p : [0,1] \to [0,1]$ is a smooth bijection.
  Then
  \[
    \int_\gamma f(z) \, dz = \int_{\gamma \circ p} f(z) \, dz.
  \]
\end{problem}

  \begin{problem}\label{identity-theorem}If $f \in \C[z]$ is a polynomial with infinitely many zeros, then
    $f \equiv 0$.
  \end{problem}
  
\end{document}
