\documentclass{homework}
\course{Math 5522H}
\author{Jim Fowler}
\input{preamble}

\begin{document}
\maketitle

\begin{inspiration}
I don't think derivatives are evil, per se --- I think they are dangerous.
\byline{Warren Buffett}
\end{inspiration}

\section{Terminology}

\begin{problem}
  What is a half-space?  Define convex hull.
\end{problem}

\begin{problem}
  Define the Wirtinger partial derivatives $\displaystyle\frac{\partial}{\partial z}$ and $\displaystyle\frac{\partial}{\partial \conj{z}}$.
\end{problem}

\begin{problem}
  What are the Cauchy-Riemann equations?
\end{problem}

\section{Numericals}

\begin{problem}\label{cauchy-riemann-polar}What are the Cauchy-Riemann equations\ldots in polar coordinates?
\end{problem}

\begin{problem}
  For a natural number $n$ define $f : \mathbb{C} \to \mathbb{C}$ by
  \[
    f(r \cos \theta + i \, r\sin \theta) = r^n \cos \left( n \theta \right) + i \, r^n \sin \left( n \theta \right).
  \]
  Use \ref{cauchy-riemann-polar} to verify that $f$ satisfies the
  Cauchy-Riemann equations.
\end{problem}

\begin{problem}
  On a certain domain, define $f(z) = \log \abs{z} + i \cdot \Arg z$
  and verify that $f$ satisfies the Cauchy-Riemann equations.
\end{problem}

\begin{problem}
  Compute $\displaystyle\frac{\partial}{\partial z} \left( z \conj{z} \right)$.
\end{problem}

\begin{problem}\label{harmonic-conjugate}Let $u(x,y) = e^y \sin x$.  Find $v(x,y)$ so that $u$ and $v$
  satisfy the Cauchy-Riemann equations.  Such a function $v$ is a
  \textbf{harmonic conjugate} of $u$.
\end{problem}

\section{Exploration}

\begin{problem}\label{cayley-transform}Relate the upper half-plane
  $H = \{ z \in \mathbb{C} : \Imag z > 0 \}$ and the open disk
  $D = \{ z \in \mathbb{C} : \abs{z} < 1 \}$ by finding $a,b,c,d \in \C$ so that the M\"obius transformation
  \[f(z) = \frac{az + b}{cz + d}\] yields a bijection $f : H \to D$.
\end{problem}

\begin{problem}\label{harmonic-necessary}Given $u : \mathbb{R}^2 \to \mathbb{R}$, is it always possible to
  find a function $v : \mathbb{R}^2 \to \mathbb{R}$ so that $u$ and
  $v$ satisfy the Cauchy-Riemann equations?
\end{problem}

\begin{problem}\label{gauss-lucas}For $p \in \C[x]$, show that the convex hull of the zeroes of $p$
  contains the zeroes of $p'$.  This is the \textbf{Gauss-Lucas
    theorem}.
\end{problem}

\begin{problem}
  Suppose the smooth function $f : \C \to \C$ satisfies the
  Cauchy-Riemann equations.  Does $f'$ also satisfy the Cauchy-Riemann
  equations?
\end{problem}

\begin{problem}
  Suppose $f : \R^2 \to \R^2$ satisfies the Cauchy-Riemann equations,
  and consider curves $\gamma_1, \gamma_2 : (-1,1) \to \R^2$ passing
  through the origin so that $\gamma_1(0) = \gamma_2(0) = (0,0)$.
  Relate the angle between the curves $\gamma_1$ and $\gamma_2$ to the
  angle between the curves $f \circ \gamma_1$ and $f \circ \gamma_2$.
  (This is related to \ref{tj-versus-jt}.)
\end{problem}

\begin{problem}
  Suppose $f : \C \to \C$ is smooth and holomorphic.  Show that the
  real part of $f$ is harmonic (cf.~\ref{harmonic-function}).
\end{problem}

\begin{problem}
  Let's redo \ref{abels-theorem} in the context of complex analysis.
  Consider a sequence $(a_n)$ of complex numbers so that
  $\sum_{n=0}^\infty a_n$ converges to $L$.  Then
  $\lim_{z \to 1^{-}} \sum_{n=0}^\infty a_n z^n = L$ provided
  $z \to 1$ in a \textbf{Stolz sector}, i.e., suppose there is some
  $K$ so that $|1-z| \leq K(1-|z|)$.
\end{problem}

\section{Prove or Disprove and Salvage if Possible}

As always with PODASIPs, many of statements below are incorrect.  For
full credit, you must not only salvage these false statements, but
also explain why the statement is false (e.g., perhaps by exhibiting a
counterexample).

\begin{problem}
  Suppose $f : \R^2 \to \R^2$ and $g : \R^2 \to \R^2$ are smooth (but
  not necessarily holomorphic when regarded as functions from $\C$ to
  $\C$).  Then by the chain rule,
  \[
    \frac{\partial}{\partial z} \left( f \circ g \right) =
    \frac{\partial f}{\partial z} \frac{\partial g}{\partial z} + \frac{\partial f}{\partial \conj{z}} \frac{\partial g}{\partial \conj{z}}.
  \]
  and similarly
  \[
    \frac{\partial}{\partial \conj{z}} \left( f \circ g \right) =
    \frac{\partial f}{\partial \conj{z}} \frac{\partial g}{\partial \conj{z}} + \frac{\partial f}{\partial z} \frac{\partial g}{\partial z}.
  \]
\end{problem}

\begin{problem}\label{schwarz-reflection-principle}If $f : \C \to \C$ is holomorphic, then $z \mapsto \overline{f(\conj z)}$ is holomorphic.
\end{problem}

\begin{problem}\label{cauchy-riemann-alone-not-sufficient}Suppose $u, v : \mathbb{R}^2 \to \mathbb{R}$ satisfy
  \[
    \frac{\partial u}{\partial x}(0,0)=\frac{\partial v}{\partial y}(0,0)
    \mbox{ and }
    \frac{\partial u}{\partial y}(0,0)=-\frac{\partial v}{\partial x}(0,0).
  \]
  Then $f : \C \to \C$ given by $f(x+iy) = u(x,y) + i \, v(x,y)$ is holomorphic at $0$.
\end{problem}

\begin{problem}\label{open-mapping-theorem-preview}There is a nonconstant holomorphic function with constant absolute value.
\end{problem}

\begin{problem}\label{schwarzian-derivative}For $f : \mathbb{C} \to \mathbb{C}$, the \textbf{Schwarzian derivative} of $f$ is
  \[ (Sf)(z)=\left({\frac{f''(z)}{f'(z)}}\right)'-{\frac12}\left(\frac{f''(z)}{f'(z)}\right)^2={\frac {f'''(z)}{f'(z)}}-{\frac32}\left(\frac{f''(z)}{f'(z)}\right)^2. \]
  If $f$ is a M\"obius transformation, then $(Sf)(z) = 0$.
\end{problem}

\end{document}
