\documentclass{homework}
\course{Math 5522H}
\author{Jim Fowler}
\input{preamble}

\begin{document}
\maketitle

\begin{inspiration}
What kind of metabolism do they have? What's their \textbf{growth rate?}
\byline{the fictional Dr. Alan Grant in \textit{Jurassic Park}, a well-known movie about complex dynamics}
\end{inspiration}

\textbf{This is a short week with an instructional break, so this
  problem set is shorter.}

\section{Terminology}

\begin{problem}
  What does it mean to say that an entire function is of
  \textbf{finite order}?
\end{problem}

\begin{problem}
  What are \textbf{canonical factors}?
\end{problem}

\section{Numericals}

\begin{problem}
  Compute $\displaystyle\prod_{n=0}^\infty \left( 1 + z^{(2^n)} \right)$.
\end{problem}

\begin{problem}
  Compute $\displaystyle\prod_{n=1}^\infty \left( 1 - \frac{1}{(2n)^2} \right)$.
\end{problem}

\begin{problem}
  What is the order of growth of $f(z) = \sin z$?
\end{problem}

\begin{problem}
  What is the order of growth of a polynomial?
\end{problem}

\section{Exploration}

\begin{problem}
  Suppose $f : \C \to \C \setminus \{0, 1\}$ is a holomorphic function
  of finite order.  What does Hadamard say about $f$ in this case?
\end{problem}

\begin{problem}
  Consider the function
  \[
    G(z) = z \prod_{n=1}^\infty \left( 1 + \frac{z}{n} \right) e^{-z/n}
  \]
  which has zeros at nonpositive integers, just like the function
  $z \mapsto 1/\Gamma(z)$ we saw last week.

  Is it the case that $1/\Gamma(z) = G(z)$?
\end{problem}

\section{Prove or Disprove and Salvage if Possible}

\begin{problem}
  A meromorphic function on the complex plane is the quotient of two
  entire functions.
\end{problem}

\begin{problem}
  If $f : \C \to \C$ is a odd function of order 1 with $f(n) = 0$ for
  $n \in \Z$, then $f(z) = \sin (\pi z)$.
\end{problem}



\end{document}
