\documentclass{homework}
\course{Math 5522H}
\author{Jim Fowler}
\input{preamble}

\begin{document}
\maketitle

\begin{inspiration}
In mathematics, existence is freedom from contradiction.
\byline{David Hilbert}
\end{inspiration}

\section{Terminology}

\begin{problem}
  What is the \textbf{Schwarz-Christoffel integral}?

  Be careful to discuss the choice of branches in the terms appearing
  in the integrand.
\end{problem}

\begin{problem}
  What is an elliptic integral?
\end{problem}

\begin{problem}
  What is the incomplete elliptic integral of the first kind?

  This integral is usually denoted by $F$, but confusingly the input
  to $F$ is sometimes called the ``parameter'' and other times called
  the ``modular angle'' and \textit{these are different}!
\end{problem}

\section{Computation}

\begin{problem}
  Find all solutions to
  \[
    \frac{1}{x} + \frac{1}{y} + \frac{1}{z} = 1
  \]
  for integers $x,y,z \in \Z$.
\end{problem}

\begin{problem}
  For $w$ in the upper half-plane, consider
  \[
    f(w) = \int_0^w  \frac{dz}{\sqrt{1-z^2}}
  \]
  where $\sqrt{1-z^2}$ is holomorphic in the upper half-plane and positive when $w \in (-1,1)$.

  The function $f$ provides a conformal map from the upper half-plane to what region?

  What is a well-known name for the function $f$?
\end{problem}

\begin{problem}
  Consider the function
  \[
    f(w) = \int_0^w  \frac{dz}{\sqrt{z} \sqrt{z+1} \sqrt{z-1}}
  \]
  which maps the upper half-plane to a square (after making appropriate branch cuts!).

  What is the side length of the square?

  \textit{Warning:} Your answer may still involve an integral.
\end{problem}

\begin{problem}
  Describe a biholomorphic map between the unit disk and the interior
  of an $n$-gon.
\end{problem}

\section{Exploration}

\begin{problem}  
  When can a holomorphic map $f : B_1(0) \to B_1(0)$ have more than two fixed points?
\end{problem}

\begin{problem}
  Can a holomorphic map $f : \C to \C$ which isn't the identity have
  more than two fixed points?
\end{problem}

\begin{problem}
  Does every holomorphic function $f : B_1(0) \to B_1(0)$ have a fixed point?
\end{problem}

\begin{problem}
  For angles $\alpha, \beta, \gamma \in (0,2\pi)$ with $\alpha + \beta + \gamma = \pi$, the function
  \[
    f(z) = \int_0^z \frac{dw}{(w-A)^{1-\alpha/\pi} (w-B)^{1-\beta/\pi}}
  \]
  maps the upper half-plane to a triangle, and extends to a map $f : H \to T$ where $H$ is the closed half-space
  \[
    H = \{ x + iy \in \C : x, y \in \R \mbox{ and } y \geq 0 \},
  \]
  and $T$ is the (closed) triangle.

  Where does $f$ send the real line?
\end{problem}

\begin{problem}
  A M\"obius transformation $g(z) = (az + b)/(cz + d)$ with
  $a,b,c,d \in \R$ sends $H$ to itself.  Consider the composition
  \[
    f^{-1} \circ g \circ f : T \to T
  \]
  to describe a map from $T$ to itself, conformal on the interior of
  $T$, which permutes the vertices of $T$.
\end{problem}

\section{Prove or Disprove and Salvage if Possible}

\begin{problem}
  A polygon's angles determine the polygon up to similarity.
\end{problem}

\begin{problem}
  Suppose $f : B_{1+\epsilon}(0) \to \C$ and if $|z| \leq 1$ then
  $|f(z)| \leq 1$.  Then $f$ has a fixed point in the unit disk
  $B_1(0)$.
\end{problem}

\begin{problem}
  There exists a surjective holomorphic function
  $f : B_1(0) \to B_1(0)$ which is not injective.
\end{problem}

\begin{problem}
  There exists a surjective holomorphic function $f : B_1(0) \to \C$.
\end{problem}

\end{document}
